A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-06 paper.tex
reply to JS

\todo[inline]{KC: KC, please add \url{https://arxiv.org/abs/2001.11560}
to this section.}

@@

\todo[inline]{JS: say something about the difference between the above
  and what is in this paper. That's the whole point of the related
  work section from the eyes of the reviewer.}  \todo[inline]{KC: I
  might have some misconcept about the related work section. You might
  have felt this, haha. Now I think this section is targeting the
  following scenarios: - ``I think someone has solved this problem
  ...''  - ``This work looks similar to paper X, what is the
  difference?''  - ``Is this work inspired by paper X?''  Is my
  understanding correct?}  \todo[inline]{JS: yes, and make sure to
  give very explicit answers to these questions. It should feel to you
  like you're hitting the reader over the head with the most obvious
  things (to you). The above paragraph is currently insufficient
  because it doesn't emphasize what scientific constributions are new
  to our paper compared to those prior papers on coercions in normal
  form.}

@@

\todo[inline]{JS: again, say something about the difference between
  the above and what is in this paper.}

@@

The transition relation \reduceto{s}{s} invokes the cast application
function, noted as $\applyCast{v}{\ccast{S}{l}{T}}$, which is also defined
by specify blame strategies (Fig.~\ref{fig:blame-strategy-LazyD} and
Fig.~\ref{fig:blame-strategy-LazyUD}).
\todo[inline]{JS: be consistent with the font used for applyCast. Sometimes
  you use roman and sometimes you used italic. Also, be consistent
  for all the metafunctions (eval, observe, etc.).}
%
When evaluating a cast expression, the machine moves the cast to the
continuation and evaluates the inner expression.
%
To cast a value, the machine invokes applyCast on the value. The cast
result is either a value or an error (\error{l}). If the cast
succeeds, the machine returns the value to the next continuation.  If
the cast fails, the machine halts with the blame label.
%
To apply a casted function, the machine first casts the argument $v$, then
applies the inner function $u$ to the casted argument, and finally
casts the return value.
%
To project the first element of a casted pair, the machine projects
the first element of the inner pair $u$ and cast it.
%
Projecting the second element of a casted pair is similar.

@@

Recall that our goal is to prove that \SMachine{C} is equivalent to
\LDMachine\ or \LUDMachine\ when $C$ satisfies some properties. The
Cast ADT specifies the behavior of identity casts and composition, so
the only remaining operator to specify is translation:
$\translate{\ccast{S}{l}{T}}$.
%
Lazy D Cast ADT (Definition~\ref{def:LazyD-CastADT}) and Lazy UD Cast ADT 
(Definition~\ref{def:LazyUD-CastADT}) specify the behavior 
of \translate{\ccast{S}{l}{T}}. Readers are encouraged to compare them with the 
corresponding $\mathrm{applyCast}$ functions 
(Fig.~\ref{fig:blame-strategy-LazyD} and 
Fig.~\ref{fig:blame-strategy-LazyUD}).
\todo[inline]{JS: what does ``them'' refer to in the previous sentence?
  Please replace with a specific noun. Also, why should the reader do
  the comparison? What are they suppose to notice?}
\todo[inline]{JS: say where the following equations come from.
  They are the equations you needed for the proof of equivalence,
  right?}

@@

\todo[inline]{There should be some text regarding the following
two theorems.}

@@

\todo[inline]{KC: (About the following paragraph) Should we mention KC and Deyaa as citation?
  (something like in private communication with KC and Deyaa)}
\todo[inline]{JS: Yes}

@@

\todo[inline]{KC: I need a better name for \compatibletailhead{t}{h}}

>>>>

\todo[inline]{KC: [IMPORTANT] KC, please add \url{https://arxiv.org/abs/2001.11560}
to this section.}

@@

\todo[inline]{KC: [IMPORTANT]}
\todo[inline]{JS: say something about the difference between the above
  and what is in this paper. That's the whole point of the related
  work section from the eyes of the reviewer.}  \todo[inline]{KC: I
  might have some misconcept about the related work section. You might
  have felt this, haha. Now I think this section is targeting the
  following scenarios: - ``I think someone has solved this problem
  ...''  - ``This work looks similar to paper X, what is the
  difference?''  - ``Is this work inspired by paper X?''  Is my
  understanding correct?}  \todo[inline]{JS: yes, and make sure to
  give very explicit answers to these questions. It should feel to you
  like you're hitting the reader over the head with the most obvious
  things (to you). The above paragraph is currently insufficient
  because it doesn't emphasize what scientific constributions are new
  to our paper compared to those prior papers on coercions in normal
  form.}

@@

\todo[inline]{JS: again, say something about the difference between
  the above and what is in this paper.}
\todo[inline]{KC: [IMPORTANT] will do.}

@@

The transition relation \reduceto{s}{s} invokes the cast application
function, noted as $\applyCast{v}{\ccast{S}{l}{T}}$, which is also defined
by specify blame strategies (Fig.~\ref{fig:blame-strategy-LazyD} and
Fig.~\ref{fig:blame-strategy-LazyUD}).
\todo[inline]{JS: be consistent with the font used for applyCast. Sometimes
  you use roman and sometimes you used italic. Also, be consistent
  for all the metafunctions (eval, observe, etc.).}
\todo[inline]{KC: [IMPORTANT] will do.}
%
When evaluating a cast expression, the machine moves the cast to the
continuation and evaluates the inner expression.
%
To cast a value, the machine invokes applyCast on the value. The cast
result is either a value or an error (\error{l}). If the cast
succeeds, the machine returns the value to the next continuation.  If
the cast fails, the machine halts with the blame label.
%
To apply a casted function, the machine first casts the argument $v$, then
applies the inner function $u$ to the casted argument, and finally
casts the return value.
%
To project the first element of a casted pair, the machine projects
the first element of the inner pair $u$ and cast it.
%
Projecting the second element of a casted pair is similar.

@@

Recall that our goal is to prove that \SMachine{C} is equivalent to
\LDMachine\ or \LUDMachine\ when $C$ satisfies some properties. The
Cast ADT specifies the behavior of identity casts and composition, so
the only remaining operator to specify is translation:
$\translate{\ccast{S}{l}{T}}$.
%
Lazy D Cast ADT (Definition~\ref{def:LazyD-CastADT}) and Lazy UD Cast ADT 
(Definition~\ref{def:LazyUD-CastADT}) specify the behavior 
of \translate{\ccast{S}{l}{T}}. Readers are encouraged to compare these two
definitions with the corresponding $\mathrm{applyCast}$ functions 
(Fig.~\ref{fig:blame-strategy-LazyD} and 
Fig.~\ref{fig:blame-strategy-LazyUD}).
\todo[inline]{JS: what does ``them'' refer to in the previous sentence?
  Please replace with a specific noun. Also, why should the reader do
  the comparison? What are they suppose to notice?}
\todo[inline]{JS: say where the following equations come from.
  They are the equations you needed for the proof of equivalence,
  right?}
\todo[inline]{KC: [IMPORTANT] will do.}

@@

\todo[inline]{JS: There should be some text regarding the following
two theorems.}

@@

\todo[inline]{KC: (About the following paragraph) Should we mention KC and Deyaa as citation?
  (something like in private communication with KC and Deyaa)}
\todo[inline]{JS: Yes}
\todo[inline]{KC: Could you show me how to do this? I don't know exactly
how to write this kind of citations.}

@@

\todo[inline]{KC: I need a better name for \compatibletailhead{t}{h},
any suggestion from Jeremy?}
